---
output: rmarkdown::github_document
---

# stringore

Tidy Regular Expression Operations with Extensive Character Encoding Support

## Description

The 'Onigmo' regular expression 'C' libary <https://github.com/k-takata/Onigmo> --- which is an extension of the 'Onigmura' <https://github.com/kkos/oniguruma> library --- provides support for a wide array of regular expression types and works across a  wide array of character encodings. Methods are provided to perform searching, matching and extraction in a tidy (i.e. "data first") manner.

[`ore`](https://github.com/jonclayden/ore) is another Onigmo-based R package for handling regular expressions (it was the first to wrap this library). It abstracts much of the complexity of Onigmo whereas the goal of `stringore` is to expose all of the features and power of Onigmo while also providing a "tidy" abstraction layer.

## NOTE

This is a WIP and the API will likely go through a few rough iterations, so do not base any "production" work on it. If you decide to live dangerously, you can use [releases](https://github.com/hrbrmstr/stringore/releases) to checkpoint your projects.

Since it is a WIP, _your_ thoughts are most welcome. Please [file an issue](https://github.com/hrbrmstr/stringore/issues) with any questions, notes, ideas, etc.

## What's Inside The Tin

The following functions are implemented:

- `onigomo_library_version`: Return the version of the Onigmo library being used by the package

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/stringore")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(stringore)

# current verison
packageVersion("stringore")

onigomo_library_version()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.